\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1cm]{geometry}
\setlength{\parindent}{0cm}
\usepackage{array}

\pagestyle{empty}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\title{Curriculum vitae}
\author{Ondrej Sika}

\begin{document}
\begin{center}
{\LARGE \bf Ondrej Sika}\\
\vspace*{0.4cm}
\begin{tabular}{R{5cm}L{5cm}}
address & Molakova 544/34\\
% & flat no. 818\\
 & 180 00 Prague\\
 & Czech Republic\\
email & \texttt{ondrej@ondrejsika.com}\\
www & \texttt{http://ondrejsika.com}\\
phone & +420 773 452 376\\
\\
citizenship & Czech Republic\\
date of birth & 25. 2. 1993\\
\end{tabular}

\vspace*{0.5cm}
{\hfill 3. 11. 2016}\\
{\hfill \texttt{https://ondrejsika.com/resume.pdf}}
\end{center}

\section*{Primary Computer skills}
{\bf Python, Django, Twisted} \\
{\bf PostgreSQL, MySQL}  \\
{\bf Bitcoin, Namecoin, Zcash, Blockchain, Mining (Cryprocurrencies)}  \\
{\bf DevOps, AWS, Puppet}

\section*{Professional experience}
\subsection*{Slush Pool - Backend Engineer (2015 - now)}
{\bf Python, Twisted, Bitcoin, Namecoin, Zcash, PostgreSQL, MySQL}

I've been working on minig backend, distributed and decentralized network application which handle 20~000 persistant connection around the globe. I've implemented Namecoin merge mining and new cryptocurrency Zcash - \texttt{https://slushpool.com}

\subsection*{\large \bf Slush Pool - Web Developer (2014 - 2015)}
{\bf Python, Django, Bitcoin, MySQL}

I worked on Django backend of Slush Pool website to get best user experience from managing your mining devices. Our website has 1~000~000 pageviews per month and is optimized to fast run from every place at the world. - \texttt{https://slushpool.com}


\subsection*{GayGuide365 - Lead Developer (2013 - 2014)}
{\bf Python, Django, PostgreSQL}\\

I was a leader of web developers team and we had build the global travel guide like Trip Advisor focused to LGBT. I designed application infrastructure and technology stack of all parts of the project, from backend to frontend. - \texttt{https://www.gayguide365.com}


\subsection*{Freelance developer \& Consultatnt (2011 - now)}
{\bf PHP, Python, Django, PostgreSQL}\\

I've done some small and medium website and web applications. I had a PHP hosting service.

\section*{Main Personal Projects}

\subsection*{Consulting and Training in Czech Republic (2015 - now)}
 I've decided to share my knowledge from engineering and software development and I've started training consulting in Czech Republic. - \texttt{https://ondrejsika.cz}

\subsection*{Git Training in Czech Republic (2013 - now)}
Git was my first step on my training career, I've think that is very important and usesful tool and a lot of czech companies still didn't using Git or using properly - \texttt{https://skoleni-git.cz}

\section*{Open Source}

I belive in Open Source, almost all my personal project are on Github. I also contribute to others open source projects to make a better software world. - \texttt{https://github.com/ondrejsika}.


\section*{Community}

\subsection*{Bitcoin Meetups in Pilsen (2016 - now)}
I've started Bitcoin Meetups in Pilsen, city I'm from. - \texttt{https://bitcoinplzen.cz}

\subsection*{Czech Bitcoin Community}
I'm also member of Czech Bitcoin Community, one of the largest and most active Bitcoin community on world. Ocassionaly I talk on the weekly meetups.

\subsection*{Python CZ, Django Girls}
In Czech Republic, we have a strong Python community. We organized monthly talks, Django Girls workshops and lot of others (Pycon CZ), ... - \texttt{https://python.cz}, \texttt{https://djangogirls.org}

\subsection*{Czechitas}
Czchitas are girs want more girls in IT. I am couch on the HTML, CSS and PHP workshops and make the GIT, Python and Bitcoin workshops for them. - \texttt{https://czechitas.cz}


\section*{Talks}

Here are some selected talks. List of all my talks with slides - \texttt{https://ondrejsika.com/talks}\\

- {\bf Merge Mining and SatoshiLabs}, Bitcoin Meetup (Bern, Switzerland)\\
- {\bf Merge Mining and Sidechains}, Bitcoin Meetup (Prague, Czech Republic)\\
- {\bf Merged Mining} (CTJB, Slovakia)


\section*{Scouting}

Scouting, scout idea and values are very important part of my life. I'm proud member of scout group Seda~Strela since 2000. From summer 2016, I'm leder of this group. - \texttt{https://sedastrela.cz}


\section*{Languages}
Czech (native), English (B2, technical), German (A1)\\

\section*{Hobbies}
Scouting, Sport flying, Yachting, Orienteering, Cycling (bike \& scooter), Reading, Math, Chess, ...
\\

\section*{Links}

- Facebook - \texttt{https://facebook.com/sikaondrej2}\\
- LinkedIn - \texttt{https://linkedin.com/in/ondrejsika}\\
- Github - \texttt{https://github.com/ondrejsika}\\
- SpeakerDeck (slides) - \texttt{https://speakerdeck.com/ondrejsika}\\

\end{document}

